GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-23 paper/kbanotebook2013/content/implementation.tex
added comments to morteza's changes

We extract aliases for entities from Wikipedia automatically both using API 
and using the actual page content, then apply pattern matching rules for slot 
value extraction.

@@

We use Wikipedia API to get some aliases automatically. This is done by 
retrieving backlink references (redirects of a wiki entity). Unfortunately 
this is not good enough and to enhance recall we need more aliases. To have 
better use of a wiki page we parse HTML DOM of the page, then use regular 
expressions to extract the bold phrases of the first paragraph as alias of the 
actual entity. Based on our observation this is a very accurate heuristic and 
provides us with lots of famous aliases of the entities. To consider other 
typical cases we consider some generic first name last name order swapping 
conventions such as Bill Gates -\textgreater Gates, Bill.

>>>>

\ceg{Instead of this paragraph we talk about what this section will
contain. We can discuss the input/output of the system too.
}
We extract aliases for entities from Wikipedia automatically both using API 
and using the actual page content, then apply pattern matching rules for slot 
value extraction.

@@

We use Wikipedia API to get some aliases automatically. This is done by 
retrieving backlink references (redirects of a wiki entity). Unfortunately 
this is not good enough and to enhance recall we need more aliases. To have 
better use of a wiki page we parse HTML DOM of the page, then use regular 
expressions to extract the bold phrases of the first paragraph as alias of the 
actual entity. Based on our observation this is a very accurate heuristic and 
provides us with lots of famous aliases of the entities. To consider other 
typical cases we consider some generic first name last name order swapping 
conventions such as Bill Gates $\rightarrow$ Gates, Bill.

### 2013-09-23 paper/kbanotebook2013/content/introduction.tex
added comments to morteza's changes

In this article we will describe the approach the GatorDSR team from the 
University of Florida takes at addressing the challenge at NIST’s Text 
REtrieval Conference (TREC) - Knowledge Base Acceleration track 2013 - Stream 
Slot Filling (SSF) section. In the first section of this article we describe 
the system design and articulate its evolution during the whole process, 
challenges and needs that we have overcome. In the second section we will go 
through the details of the NLP techniques we took at streaming slot filling
(SSF): given a slot name (entity + relation type) we fill in the slot value
(relation value) on structured text documents.

The task is that given certain Wikipedia or Twitter entities 
(wiki/twitter URLs) and certain relations of interest given in Table 1, 
extract as many triple relations as possible (hence, slot filling). This can 
be used to automatically populate knowledgebases such as free-base or DBPedia 
or even filling in the information boxes at Wikipedia. The corpus is in 
English and is a snapshot of part of the web containing arXiv, social, news, 
linking, weblog, forum, classifieds, reviews, and memetracker documents. Each 
document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields.

@@

>>>>

In this article we will describe the approach the GatorDSR team from the 
University of Florida in addressing the challenge at NIST’s Text 
REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013 
In the first section we describe 
the system design and articulate its evolution during the whole process, 
challenges and needs that we have overcome. In the second section we will go 
through the details of the NLP techniques we took at streaming slot filling
(SSF): given a slot name (entity + relation type) we fill in the slot value
(relation value) on structured text documents.

\ceg{Add a discussion of why machine driven kb population is important.}
The task is that given certain Wikipedia or Twitter entities 
(wiki/twitter URLs) and certain relations of interest given in Table 1, 
extract as many triple relations as possible (hence, slot filling). This can 
be used to automatically populate knowledgebases such as free-base or DBPedia 
or even filling in the information boxes at Wikipedia. The corpus is in 
English and is a snapshot of part of the web containing arXiv, social, news, 
linking, weblog, forum, classifieds, reviews, and memetracker documents. Each 
document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields.

@@

\ceg{How will each submission be evaluated?}

### 2013-09-23 paper/kbanotebook2013/content/system.tex
added comments to morteza's changes

In this section we provide a high level description of the pipeline(system) 
design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
task. Our pipeline of processing the corpus consists of a two layer indexing 
system main section in our system regarding indexing the corpus, We started 
off by trying to use the off-the-shelf tools for this task. Mainly we started 
by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
performance there.  Spark was not as efficient as expected and the overhead 
was much more than tolerable. We tried to use Scala parallelization itself to 
do the job, and unfortunately it did not satisfy our needs, there was 
excessive memory overhead on map reduce jobs. We migrated the core of the 
system to Java Parallelism APIs and that was not good enough either, we wanted 
better. So we built our own parallel system which in actual performance had 
the least of overhead, the least memory consumption and the most robust memory 
model which avoided unpredictable CPU stalls on garbage collections in 
processing the corpus. In what follows we will describe each step of this 
evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
system. The platform that we run our pipeline over was a 32 core server having 
64GB of memory.

@@

Regarding Cumulative Citation Recommendation we perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable.
For future iterations of the paper we have ideas on how to score documents 
based on their likelihood of citation worthiness but for this iterations we 
treat all mentioning documents equally likely. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have highly low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents. Regarding mentioning but 
garbage, neutral or central documents we produce more slot values which can be 
later on filtered out in the high accuracy filter section.

\subsection{Streaming Slot Filling}

Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

>>>>

\ceg{Discuss current system first. If you want to keep the decisions points
that led to the current architecture, make it a subsection.}
In this section we provide a high level description of the pipeline(system) 
design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
task. Our pipeline of processing the corpus consists of a two layer indexing 
system main section in our system regarding indexing the corpus, We started 
off by trying to use the off-the-shelf tools for this task. Mainly we started 
by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
performance there.  Spark was not as efficient as expected and the overhead 
was much more than tolerable. We tried to use Scala parallelization itself to 
do the job, and unfortunately it did not satisfy our needs, there was 
excessive memory overhead on map reduce jobs. We migrated the core of the 
system to Java Parallelism APIs and that was not good enough either, we wanted 
better. So we built our own parallel system which in actual performance had 
the least of overhead, the least memory consumption and the most robust memory 
model which avoided unpredictable CPU stalls on garbage collections in 
processing the corpus. In what follows we will describe each step of this 
evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
system. The platform that we run our pipeline over was a 32 core server having 
64GB of memory.

@@

\ceg{This section should be structured as follows:
1: Introduce CCR (Motivation, Expectations)
2: Our high level approach
3: Discussion of our design (Like already discussed)
}
Regarding Cumulative Citation Recommendation we perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable.
For future iterations of the paper we have ideas on how to score documents 
based on their likelihood of citation worthiness but for this iterations we 
treat all mentioning documents equally likely. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have highly low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents. Regarding mentioning but 
garbage, neutral or central documents we produce more slot values which can be 
later on filtered out in the high accuracy filter section.

\subsection{Streaming Slot Filling}
\ceg{See the previous note.}
Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.
